\documentclass[conference]{IEEEtran}
%\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

%\addtolength{\oddsidemargin}{-.875in}
%\addtolength{\evensidemargin}{-.875in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{-.875in}
%\addtolength{\textheight}{1.75in}
	
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{automata,positioning}
\usepackage{url}
\usepackage{float}
\usepackage{setspace}
\usepackage{filecontents,lipsum}
\usepackage[noadjust]{cite}
\usepackage{listings}

\begin{document}
%\raggedright
%\doublespacing

\title{Week 4 Journal}
\author{Rodger Byrd}
\maketitle


\section{Overview}
For my area I'm looking at Anti-Patterns in code, these are also known as code smells. I've also seen them referred to as Atoms of Confusion and nano patterrns.

\section{Journal Entry}
This week I primarily focused on finding recent papers to include in my survey.
I decided to focus on papers that have been published since the last surver paper of 2018.
I think I should be able to find papers from 2017 to present time.

Additionally, I think there are some interesting areas that aren't covered in the previous survey papers, such as tools for detecting code smells and anti-patterns as well as how to correct or re-write anti-patterns in code.

One thing I want to focus on is very recent relevant papers.
Fortunately google scholar allows you to researc only papers that have been written since a particular year.

The files for this latex document are in the github repository located at \path{https://github.com/rodger79/CS6000}

Relevan papers are referenced in the bibliography below. 
\nocite{*}
\clearpage


\bibliographystyle{IEEEtran}
\bibliography{references}


\end{document}