\documentclass[conference]{IEEEtran}
%\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

%\addtolength{\oddsidemargin}{-.875in}
%\addtolength{\evensidemargin}{-.875in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{-.875in}
%\addtolength{\textheight}{1.75in}
	
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{automata,positioning}
\usepackage{url}
\usepackage{float}
\usepackage{setspace}
\usepackage{filecontents,lipsum}
\usepackage[noadjust]{cite}
\usepackage{listings}

\begin{document}
%\raggedright
%\doublespacing

\title{Week 8 Journal}
\author{Rodger Byrd}
\maketitle


\section{Overview}
For my area I'm looking at Anti-Patterns in code, these are also known as code smells. I've also seen them referred to as Atoms of Confusion and nano patterrns.

\section{Journal Entry}
This week I continued working on the draft paper. After my first draft, I realized that the training of the machine learning algorithms is an inportant aspect to cover, and I'll have to redo some sections based on that. Also, I think I could have gone into more detail on many of the papers so I'm working on rereading some of the cited papers to do that. 

I reviewed one of the 2 papers assigned "Promoting Collaborative Critical Infrastructure Defenese in a Changing World" by Jennifer Smith, but I had problems with canvas. The other paper that came up for me was "Survey Paper Draft" by Manohar Raavi. I don't currently see any actions in canvas at this time for either paper. 

%The files for this latex document are in the github repository located at \path{https://github.com/rodger79/CS6000}

%Relevan papers are referenced in the bibliography below. 
\nocite{*}
\clearpage


%\bibliographystyle{IEEEtran}
%\bibliography{references}


\end{document}