\documentclass[conference]{IEEEtran}
%\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

%\addtolength{\oddsidemargin}{-.875in}
%\addtolength{\evensidemargin}{-.875in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{-.875in}
%\addtolength{\textheight}{1.75in}
	
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{automata,positioning}
\usepackage{url}
\usepackage{float}
\usepackage{setspace}
\usepackage{filecontents,lipsum}
\usepackage[noadjust]{cite}
\usepackage{listings}

\begin{document}
%\raggedright
%\doublespacing

\title{Week 6 Journal}
\author{Rodger Byrd}
\maketitle


\section{Overview}
For my area I'm looking at Anti-Patterns in code, these are also known as code smells. I've also seen them referred to as Atoms of Confusion and nano patterrns.

\section{Journal Entry}
This week I continued finding recent papers to include in my survey. 
I decided to focus on recent (2018 and 2019) papers that have been published since the last surver paper of 2018 because it was a good survey.
One very interesting thing that was previously missing from the other papers was machine learning.
This week I spent most of the time looking for papers releated to using machine learning to correct or detect anti-patterns and code smells in code. 
I found quite a few different papers so I think this will probably be the primary focus of my survey paper that I've started drafting.

The files for this latex document are in the github repository located at \path{https://github.com/rodger79/CS6000}

Relevan papers are referenced in the bibliography below. 
\nocite{*}
\clearpage


\bibliographystyle{IEEEtran}
\bibliography{references}


\end{document}